Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
added running example for the multi-staged verif approach

\end{enumerate}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with abstraction refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

\subsubsection{Illustrative Example} \label{sec:running-ex}

We illustrate our approach with \todo{what example is this?} example,
extracted from the literature~\cite{?}.
%% Next, we demonstrate how our approach solves the synthesis problem for this
%% example.

We start with a candidate solution with all coefficients zero, $K=[0
  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
{\sc verify} stage, the {\sc safety} check finds the counterexample
%
$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
%
After adding the new counterexample to its sets of {\sc inputs}, {\sc
  synthesize} finds the candidate solution $K=[0 \ 0
  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.

In the subsequent iteration, the synthesiser can't find any more
candidates and returns UNSAT, meaning that the current precision is
insufficient.  Consequently, we increase the precision to $I_p=17$,
$F_p=7$.
%
Since the previous counterexamples were obtained at lower precision,
we remove them from the set of counterexamples.  Back in the {\sc
  synthesize} phase, we re-start the process with a candidate solution
with all coefficients $0$.  Next, the {\sc safety} verification stage
provides the first counterexample at higher precision, $x_0=[-0.5
  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
However, this candidate triggers the counterexample
$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
stage.  In the next iteration, we get the candidate $K=[0 \ 0
  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
  \ 0.5]$. Finally, {\sc synthesize} find the candidate $K=[0.01171875
  \ -0.013671875 \ -0.013671875]$, which is validated as a final
solution by all the verification stages.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with abstraction refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
